Neural Network Language Models for Automatic Speech Recognition

### 2018-12-12 paper/paper.tex
paper: Make wikitext and gigaword subsections
paper: Fix emph
paper: Fix duplicate label
paper: Escape &

\section{WikiText}
\label{sec:wikitext}

@@

\section{Gigaword}
\label{sec:gigaword}

@@

"US business leaders lashed out wednesday at legislation that would penalize companies
\epmh{for employing illegal immigrants}."

@@

\subsection{RNN}
\label{sec:lstm}

@@

We found that like the paper suggested, usage of regularization techniques did not assist in improving
either perplexity or scores on both METEOR and ROUGE. This was even true in the case of Dropout,
which was proposed after the 2010 paper by Milkolov was published. Such a result was surprising to us
and perhaps requires further investigation and testing. For instance, Zaremba & Vinyals found that
applying dropout on non-recurrent connections could be an effective regularizer \cite{zaremba2015},
though this is different to the way in which we implemented dropout, which was on both the recurrent
and non-recurrent connections. This may have impacted the network's ability to remember crucial
information during training that it would allow it to make better predictions and optimize better.

>>>>

\subsection{WikiText}
\label{sec:wikitext}

@@

\subsection{Gigaword}
\label{sec:gigaword}

@@

"US business leaders lashed out wednesday at legislation that would penalize companies
\emph{for employing illegal immigrants}."

@@

\subsection{RNN}
\label{sec:rnn}

@@

We found that like the paper suggested, usage of regularization techniques did not assist in improving
either perplexity or scores on both METEOR and ROUGE. This was even true in the case of Dropout,
which was proposed after the 2010 paper by Milkolov was published. Such a result was surprising to us
and perhaps requires further investigation and testing. For instance, Zaremba 'I\&' Vinyals found that
applying dropout on non-recurrent connections could be an effective regularizer \cite{zaremba2015},
though this is different to the way in which we implemented dropout, which was on both the recurrent
and non-recurrent connections. This may have impacted the network's ability to remember crucial
information during training that it would allow it to make better predictions and optimize better.
